### 2021-03-11 results/draft.tex
revised the objectives

\newpage
\begin{linenumbers}
\setstretch{2}
\section{Introduction}
Understanding of spatial distribution of species and underling its mechanism is a major goal in ecology. 
Field surveys using environmental DNA (eDNA) are widely used for detecting invasive or rare species and hotspot of biodiversity %(面倒なのでレビュー論文を引用) 
because the surveys of eDNA are easy to detect occurrence of target species, non-invasiveness, and high cost effectiveness rather than previous direct sampling method (Rees et al. 2014; Thomsen \& Willerslev 2015) %Dorazioに引用されていたやつ．あとで再確認
However, uncertainty of the occurrence of eDNA is a issue in eDNA studies because various factors, such as biological and environmental features, intricately affect the shedding (i.e., production of eDNA from organisms) and degradation (i.e., decay of eDNA from a system) of eDNA (Fig. 1). Therefore, it is necessary to consider the spatial uncertainty included in eDNA to estimate the spatial distribution of species.

@@

\ \ \ \ \ \ \ \ \ \ 
In this paper, to predict spatial distribution of species from eDNA, we first make a model which considers uncertainties of eDNA caused by environmental factors without additional laboratory experiments and numerical hydrodynamic models, by using an integrated spatial distribution model (eDNA-IDM). We then apply the model to both eDNA data and catch statistics for four Edomae fish in Tokyo Bay, Japan. 
The predicted spatial distribution of four fish form our model reduced

>>>>

\newpage
\begin{linenumbers}
\setstretch{2}
\section{Introduction}
Understanding of spatial distribution of species and underling its mechanism is a major goal in ecology. 
Field surveys using environmental DNA (eDNA) are widely used for detecting invasive or rare species and hotspot of biodiversity %(面倒なのでレビュー論文を引用) 
because the surveys of eDNA are easy to detect occurrence of target species, non-invasiveness, and high cost effectiveness rather than previous direct sampling method (Rees et al. 2014; Thomsen \& Willerslev 2015) %Dorazioに引用されていたやつ．あとで再確認
However, uncertainty of the occurrence of eDNA is a issue in eDNA studies because various factors, such as biological and environmental features, intricately affect the shedding (i.e., production of eDNA from organisms) and degradation (i.e., decay of eDNA from a system) of eDNA (Fig. 1). Therefore, it is necessary to consider the spatial uncertainty included in eDNA to infer the spatial distribution of species.

@@

\ \ \ \ \ \ \ \ \ \ 
In this paper, 
%to predict spatial distribution of species from eDNA, we first make a model which considers uncertainties of eDNA caused by environmental factors without additional laboratory experiments and numerical hydrodynamic models, by using an integrated spatial distribution model (eDNA-IDM). 
to infer spatial distribution of species from eDNA, we first make a spatial distribution model wichi considers spatial uncertainty of eDNA by using an integrated spatial distribution model. 
We then apply the model to both eDNA data and catch statistics for four Edomae fish in Tokyo Bay, Japan. 
%The predicted spatial distribution of four fish form our model reduced
